Digitization of the Australian Parliamentary Debates, 1998-2022

### 2023-08-04 paper/paper-nature-revised.qmd
small changes, updated bib

The official written record of parliamentary debates, formally known as Hansard [@citehansard], plays a fundamental role in capturing the history of political proceedings and facilitating the exploration of valuable research questions. Originating in the British parliament, the production of Hansard became tradition in many other Commonwealth countries, such as Canada and Australia [@vice2017history]. Given the content and magnitude of these records, they have significance, particularly in the context of political science research. In the case of Canada, the Hansard has been digitized for 1901 to 2019 [@lipad]. Having a digitized version of Hansard enables researchers to conduct text analysis and statistical modelling. Following the lead of that project, in this paper we introduce a similar database for Australia. This is composed of individual datasets for each sitting day in the House of Representatives from 1998 to September 2022, containing details on everything said in parliament in a form that can be readily used by researchers. With the development of tools for large-scale text analysis, this database will serve as a resource for understanding political behaviour in Australia over time.

@@

At present, the Hansard format that is available on the Parliament of Australia website is not easily accessible for large scale analysis. To this point, various researchers have had to create their own databases of usable, complete data based on content from the Australian Parliament website. For instance, an online, easy to read database of Hansard from 1901 to 1980 using the XML files has been created [@sherratt]. These data can be navigated by year, parliament, people, and bills [@sherratt]. To make the Australian Parliamentary Handbook more accessible, an `R` package which includes data on all MPs from 1945 to 2019 has been created @Leslie_2021_HoR_Aus. Further, there is the `AustralianPoliticians` `R` package, which contains several datasets related to the political and biographical information of Australian federal politicians who were active between 1901 and 2021 @auspol. And finally, there has been examination of speech and MP level data between 1990 and 2019 in Australia @Dowding2021. Like us they scrape the Hansard record and link it with biographical data. The key difference is that our focus is on the database itself, while they are focused on using a database constructed from the same source to answer a particular question about speaker time. This different focus leads to different emphasis and approaches.

@@

The outer-most node, also known as the parent node, is denoted `<hansard>` and serves as a container for the entire document. This parent node may have up to four child nodes, where the first child node contains details on the specific sitting day. Next, `<chamber.xscript>` contains all proceedings of the Chamber, `<fedchamb.xscript>` contains all proceedings of the Federation Chamber, and `<answers.to.questions>` contains Question Time proceedings. The Federation Chamber does not meet on every sitting day, so this child element is not present in every XML file. The use of separate child nodes allows for the distinction of proceedings between the Chamber and Federation Chamber. The structure of the `<chamber.xscript>` and `<fedchamb.xscript>` nodes are generally the same, where the proceeding begins with `<business.start>` which is followed by a series of debates. Debate nodes can contain a `<subdebate.1>` child node which has a `<subdebate.2>` child node nested within it. That said, sometimes `<subdebate.2>` is not nested within `<subdebate.1>`. Each of these three elements (i.e. `<debate>`, `<subdebate.1>`, and `<subdebate.2>`) as well as their respective sub-elements contain important information on the topic of discussion, who is speaking, and what is being said. The `<speech>` node within each one contains the bulk of the text associated with that debate or sub-debate. A typical `<speech>` node begins with a `<talk.start>` sub-node, providing information on the MP whose turn it is to speak and the time of their first statement. Unsurprisingly, speeches rarely go uninterrupted in parliamentary debate settings --- they are often composed of a series of interjections and continuations. These statements are categorized under different sub-nodes depending on their nature, such as `<interjection>` or `<continuation>`. The final key component of Hansard is Question Time, in which questions and answers are classified as unique elements. More detail on the purpose and processing of Question Time will [follow](#sec-qa).

@@

The next step was to further develop our script to produce tidy data sets, as defined and introduced by @Wickham2014. These contain all parsed text elements, where each statement is separated onto its own row with details about the MP who is speaking, and rows are maintained in chronological order. This first involved correcting the variable classes and adding several indicator variables to differentiate where statements came from, such as Chamber versus Federation Chamber or `<subdebate.1>` versus `<subdebate.2>`. The next key task stemmed from the fact that the raw text data were not separated by each statement when parsed. In other words, any interjections, comments made by the Speaker or Deputy Speaker and continuations within an individual speech were all parsed together as a single string. As such, the name, name ID, electorate and party details were only provided for the person whose turn it was to speak. There were many intricacies in the task of splitting these speeches in a way that would be generalizable across sitting days. Details on these are provided in the Interjections [section](#sec-interject) to follow.

Since we are looking at a wide time span of documents, there are many changes in the way they are formatted. These became apparent as we ran our script on XML files from earlier sitting days. Some changes are as subtle as a differently named child node, while others are as extensive as a completely different nesting structure. Smaller changes were accounted for as we became aware of them, and embedded into the code in a way that would not cause issues for parsing more current Hansards with subtle differences in formatting. However, as mentioned, more significant changes in the XML structure of Hansard are what necessitated the development of separate scripts as we worked backwards. Further not every sitting day contains every possible XML element. For example, some days did not have `<subdebate.2>` content, and some days did not have a Federation Chamber proceeding. To improve the generalizability of these scripts, if-else statements were embedded within the code wherever an error might arise due to a missing element. For example, the entire Federation Chamber block of code is wrapped in an if-else statement for each script, so that it only executes if what the code attempts to parse exists in the file.

Once the script ran without error for a few recent years of Hansard, we continued to work backwards until extensive changes in tree structure made our script incompatible with parsing earlier XML files. The earliest sitting day this first script can successfully parse is 14 August 2012. Before developing new scripts to parse earlier Hansard documents, we prioritized cleaning and finalizing what we had been able to parse. As such we continued building our script, fixing any problems we noticed in the resulting datasets such as excess whitespace or spacing issues, and splitting up any additional sections of the parsed text onto separate rows where necessary. Specifically, we added a section of our script to separate out general stage directions. More information on this separation will be provided in the subsequent Stage Directions [section](#sec-stage). After completing our first script, it was formatted as a function which takes a single file name argument and produces one CSV file containing data on all proceedings from the given sitting day.

@@

As mentioned, we developed a total of four scripts to parse the 1998-2022 time frame of Hansard documents. Two main factors motivated us to create four scripts as opposed to just one, the first being structural variation in XML over time, and the second being improved computational efficiency with separate scripts. While all four scripts use the same general approach to parsing described in the Overview [section](#sec-overview) and produce the same CSV structure, the first and second scripts use a different method of data processing than the third and fourth scripts.

@@

Once we finalized this new method of processing the data, we proceeded with data cleaning using the same general approach as in the first two scripts to produce the same structure of CSV output. We then worked backwards in time and modified the code as needed for generalizability. Throughout this process we found many transcription errors present in the XMLs from earlier years. We fixed these manually, deferring to the official release to ensure the correct information was filled in. Since there were a number of transcription errors specific to the 2000s, we chose to create a fourth script for parsing 1998 and 1999. This allowed us to remove all the code which was needed to resolve specific transcription errors of the 2000s, to avoid an overly long script and in turn improving computational efficiency. As such, our fourth script is essentially the same as the third, with the only difference being that it has code specific to fixing transcription errors from 1998 and 1999.

@@

As mentioned in the Script Differences [section](#sec-diff), more recent years of Hansard XMLs contain a series of child nodes which exist to capture the structure of interruptions in that speech. @fig-xml2 provides an example of this, where the speech was interrupted by a comment from the Deputy Speaker, and then the MP continued their speech. Looking at the element names highlighted in blue, these child nodes do not contain the actual text for the interjection or continuation --- this text is embedded within the speech above it. However, as shown by the content highlighted in pink in @fig-xml2, we were able to extract useful details on the individual interjecting which we could use later. Making use of this structure, we extracted names and information of all individuals that were categorized within the XML as interjections. We stored this as a dataframe called `"interject"`. We decided not to include this data in our final database, as it is embedded in our resulting datasets which have a flag for interjections.

@@

Having developed a successful methodology for splitting interjections, we used this to inform our general approach in the third and fourth scripts. However, the difference in data cleaning used in these scripts necessitated some departure from the original methodology. As discussed in the Script Differences [section](#sec-diff), we used string patterns extracted from `<talk.start>` nodes to separate speeches. As evident in @fig-xml2, `<talk.start>` nodes are nested within `<interjection>` nodes, meaning that the patterns of data from interjection statements were separated out in the process. In other words, our approach to data cleaning in the third and fourth scripts separated out interjections in the process. This meant that we did not need to create lists of names and titles for which to search in the text as we did before. However, we used the same list of general interjection statements on which to separate as was used in the first two scripts. We then did an additional check for statements that may have not been separated due to how they were embedded in the XML, and separated those out where needed. In particular, while most statements were categorized in their own child node and hence captured through pattern-based separation, some were not individually categorized, and had to be split manually in this step.

@@

In the Hansard XML files, divisions data are structured outside of the `<speech>` content in their own `<division>` nodes that contain the voting data and division result. Since we focus primarily on the spoken `<speech>` Hansard content, our parsing scripts do not necessarily capture all divisions data from House proceedings. Our approach to parsing Hansard in the third and fourth scripts described in the Script Differences [section](#sec-diff) naturally allowed for much of the divisions data to be added to our resulting files for 1998 to March 2011, however the parsing scripts used for May 2011 to September 2022 Hansard did not. To supplement our database and in an effort to fill this divisions data gap, we created an additional file containing all divisions data nested under the XPath "`//chamber.xscript//division`" from the Hansard files in our time frame. To produce this data file, for each Hansard XML we parsed the `<division.header>`, `<division.data>`, and `<division.result>` child-nodes where they existed, extracted any timestamps where available, and did any additional data cleaning as necessary. We used a series of if-else statements in this script to account for variation in the structure of the `<division>` node over time. Finally, we then added a date variable to distinguish between sitting days.

@@

To enhance the usability of our database, we added a `uniqueID` variable to each file. This serves as a unique identifier for each speaking MP, and comes from the `uniqueID` variable present within data from both the `AustralianPoliticians` and `AustralianElections` R packages [@auspol; @auselect]. By including this variable, one can readily integrate our data records with those available in these two packages. Similarly, we added the `partyfacts_id` variable to our data which allows users to link our data to external political party data sources with this unique identifier.

Further, the `name.id` variable found in each file is another unique identifier for each MP. This variable was parsed directly from the Hansard XML files, and can be found in the Australian Parliamentary Handbook. As such, our data records can be integrated with those from the `ausPH` package which provides datasets for contents of the Australian Parliamentary Handbook [@Leslie_2021_HoR_Aus]. This will allow for convenient extraction of further details on each MP in a tidy, ready to analyze format.

@@

The code written to build this database is available on the GitHub repository associated with this paper (https://github.com/lindsaykatz/hansard-proj). All scripts were created using R software [@r_software]. The core packages used to develop these scripts are: the `XML` package @XML_pkg, the `xml2` package @xml2_pkg, the `tidyverse` R packages @tidyverse, the `AustralianPoliticians` package @auspol, and the `ausPH` package @Leslie_2021_HoR_Aus. `XML` and `xml2` were used for parsing the XML documents, `AustralianPoliticians` and `ausPH` were used for cleaning up and filling in MP details in the datasets, and `tidyverse` packages were used in all steps, for tidy wrangling of data.

>>>>

The official written record of parliamentary debates, formally known as Hansard [@citehansard], plays a fundamental role in capturing the history of political proceedings and facilitating the exploration of valuable research questions. Originating in the British parliament, the production of Hansard became tradition in many other Commonwealth countries, such as Canada and Australia [@vice2017history]. Given the content and magnitude of these records, they have significance, particularly in the context of political science research. In the case of Canada, the Hansard has been digitized for 1901 to 2019 [@lipad]. Having a digitized version of Hansard enables researchers to conduct text analysis and statistical modelling. Following the lead of that project, in this paper we introduce a similar database for Australia. This is composed of individual datasets for each sitting day in the House of Representatives from March 1998 to September 2022, containing details on everything said in parliament in a form that can be readily used by researchers. With the development of tools for large-scale text analysis, this database will serve as a resource for understanding political behaviour in Australia over time.

@@

At present, the Hansard format that is available on the Parliament of Australia website is not easily accessible for large scale analysis. To this point, various researchers have had to create their own databases of usable, complete data based on content from the Australian Parliament website. For instance, an online, easy to read database of Hansard from 1901 to 1980 using the XML files has been created (http://historichansard.net/). These data can be navigated by year, parliament, people, and bills. To make the Australian Parliamentary Handbook more accessible, an `R` package which includes data on all MPs from 1945 to 2019 has been created (https://github.com/palesl/AustralianHouseOfRepresentatives). Further, there is the `AustralianPoliticians` `R` package, which contains several datasets related to the political and biographical information of Australian federal politicians who were active between 1901 and 2021 @auspol. And finally, there has been examination of speech and MP level data between 1990 and 2019 in Australia @Dowding2021. Like us they scrape the Hansard record and link it with biographical data. The key difference is that our focus is on the database itself, while they are focused on using a database constructed from the same source to answer a particular question about speaker time. This different focus leads to different emphasis and approaches.

@@

The outer-most node, also known as the parent node, is denoted `<hansard>` and serves as a container for the entire document. This parent node may have up to four child nodes, where the first child node contains details on the specific sitting day. Next, `<chamber.xscript>` contains all proceedings of the Chamber, `<fedchamb.xscript>` contains all proceedings of the Federation Chamber, and `<answers.to.questions>` contains Question Time proceedings. The Federation Chamber does not meet on every sitting day, so this child element is not present in every XML file. The use of separate child nodes allows for the distinction of proceedings between the Chamber and Federation Chamber. The structure of the `<chamber.xscript>` and `<fedchamb.xscript>` nodes are generally the same, where the proceeding begins with `<business.start>` which is followed by a series of debates. Debate nodes can contain a `<subdebate.1>` child node which has a `<subdebate.2>` child node nested within it. That said, sometimes `<subdebate.2>` is not nested within `<subdebate.1>`. Each of these three elements (i.e. `<debate>`, `<subdebate.1>`, and `<subdebate.2>`) as well as their respective sub-elements contain important information on the topic of discussion, who is speaking, and what is being said. The `<speech>` node within each one contains the bulk of the text associated with that debate or sub-debate. A typical `<speech>` node begins with a `<talk.start>` sub-node, providing information on the MP whose turn it is to speak and the time of their first statement. Unsurprisingly, speeches rarely go uninterrupted in parliamentary debate settings --- they are often composed of a series of interjections and continuations. These statements are categorized under different sub-nodes depending on their nature, such as `<interjection>` or `<continuation>`. The final key component of Hansard is Question Time, in which questions and answers are classified as unique elements. More detail on the purpose and processing of Question Time will follow.

@@

The next step was to further develop our script to produce tidy data sets [@Wickham2014]. These contain all parsed text elements, where each statement is separated onto its own row with details about the MP who is speaking, and rows are maintained in chronological order. This first involved correcting the variable classes and adding several indicator variables to differentiate where statements came from, such as Chamber versus Federation Chamber or `<subdebate.1>` versus `<subdebate.2>`. The next key task stemmed from the fact that the raw text data were not separated by each statement when parsed. In other words, any interjections, comments made by the Speaker or Deputy Speaker and continuations within an individual speech were all parsed together as a single string. As such, the name, name ID, electorate and party details were only provided for the person whose turn it was to speak. There were many intricacies in the task of splitting these speeches in a way that would be generalizable across sitting days. Details on these are provided later.

Since we are looking at a wide time span of documents, there are many changes in the way they are formatted. These became apparent as we ran our script on XML files from earlier sitting days. Some changes are as subtle as a differently named child node, while others are as extensive as a different nesting structure. Smaller changes were accounted for as we became aware of them, and embedded into the code in a way that would not cause issues for parsing more current Hansards with subtle differences in formatting. However, as mentioned, more significant changes in the XML structure of Hansard necessitated the development of separate scripts as we worked backwards. Further not every sitting day contains every possible XML element. For example, some days did not have `<subdebate.2>` content, and some days did not have a Federation Chamber proceeding. To improve the generalizability of these scripts, if-else statements were embedded within the code wherever an error might arise due to a missing element. For example, the entire Federation Chamber block of code is wrapped in an if-else statement for each script, so that it only executes if what the code attempts to parse exists in the file.

Once the script ran without error for a few recent years of Hansard, we continued to work backwards until extensive changes in tree structure made our script incompatible with parsing earlier XML files. The earliest sitting day this first script can successfully parse is 14 August 2012. Before developing new scripts to parse earlier Hansard documents, we prioritized cleaning and finalizing what we had been able to parse. As such we continued building our script, fixing any problems we noticed in the resulting datasets such as excess whitespace or spacing issues, and splitting up any additional sections of the parsed text onto separate rows where necessary. Specifically, we added a section of our script to separate out general stage directions. More information on this separation will be provided in the Stage Directions section. After completing our first script, it was formatted as a function which takes a single file name argument and produces one CSV file containing data on all proceedings from the given sitting day.

@@

As mentioned, we developed a total of four scripts to parse the 1998-2022 time frame of Hansard documents. Two main factors motivated us to create four scripts as opposed to just one, the first being structural variation in XML over time, and the second being improved computational efficiency with separate scripts. While all four scripts use the same general approach to parsing described in the Overview section and produce the same CSV structure, the first and second scripts use a different method of data processing than the third and fourth scripts.

@@

Once we finalized this new method of processing the data, we proceeded with data cleaning using the same general approach as in the first two scripts to produce the same structure of CSV output. We then worked backwards in time and modified the code as needed for generalizability. Throughout this process we found a number of transcription errors present in the XMLs from earlier years. We fixed these manually, deferring to the official release to ensure the correct information was filled in. Since there were a number of transcription errors specific to the 2000s, we chose to create a fourth script for parsing 1998 and 1999. This allowed us to remove all the code which was needed to resolve specific transcription errors of the 2000s, to avoid an overly long script and in turn improving computational efficiency. As such, our fourth script is essentially the same as the third, with the only difference being that it has code specific to fixing transcription errors from 1998 and 1999.

@@

As mentioned earlier, more recent years of Hansard XMLs contain a series of child nodes which exist to capture the structure of interruptions in that speech. @fig-xml2 provides an example of this, where the speech was interrupted by a comment from the Deputy Speaker, and then the MP continued their speech. Looking at the element names highlighted in blue, these child nodes do not contain the actual text for the interjection or continuation --- this text is embedded within the speech above it. However, as shown by the content highlighted in pink in @fig-xml2, we were able to extract useful details on the individual interjecting which we could use later. Making use of this structure, we extracted names and information of all individuals that were categorized within the XML as interjections. We stored this as a dataframe called `"interject"`. We decided not to include this data in our final database, as it is embedded in our resulting datasets which have a flag for interjections.

@@

Having developed a successful methodology for splitting interjections, we used this to inform our general approach in the third and fourth scripts. However, the difference in data cleaning used in these scripts necessitated some departure from the original methodology. As discussed earlier, we used string patterns extracted from `<talk.start>` nodes to separate speeches. As evident in @fig-xml2, `<talk.start>` nodes are nested within `<interjection>` nodes, meaning that the patterns of data from interjection statements were separated out in the process. In other words, our approach to data cleaning in the third and fourth scripts separated out interjections in the process. This meant that we did not need to create lists of names and titles for which to search in the text as we did before. However, we used the same list of general interjection statements on which to separate as was used in the first two scripts. We then did an additional check for statements that may have not been separated due to how they were embedded in the XML, and separated those out where needed. In particular, while most statements were categorized in their own child node and hence captured through pattern-based separation, some were not individually categorized, and had to be split manually in this step.

@@

In the Hansard XML files, divisions data are structured outside of the `<speech>` content in their own `<division>` nodes that contain the voting data and division result. Since we focus primarily on the spoken `<speech>` Hansard content, our parsing scripts do not necessarily capture all divisions data from House proceedings. Our approach to parsing Hansard in the third and fourth scripts described in the Script Differences section naturally allowed for much of the divisions data to be added to our resulting files for 1998 to March 2011, however the parsing scripts used for May 2011 to September 2022 Hansard did not. To supplement our database and in an effort to fill this divisions data gap, we created an additional file containing all divisions data nested under the XPath "`//chamber.xscript//division`" from the Hansard files in our time frame. To produce this data file, for each Hansard XML we parsed the `<division.header>`, `<division.data>`, and `<division.result>` child-nodes where they existed, extracted any timestamps where available, and did any additional data cleaning as necessary. We used a series of if-else statements in this script to account for variation in the structure of the `<division>` node over time. Finally, we then added a date variable to distinguish between sitting days.

@@

To enhance the usability of our database, we added a `uniqueID` variable to each file. This serves as a unique identifier for each speaking MP, and comes from the `uniqueID` variable present within data from both the `AustralianPoliticians` [@auspol] and `AustralianElections` R packages (https://github.com/RohanAlexander/AustralianElections). By including this variable, one can integrate our data records with those available in these two packages. Similarly, we added the `partyfacts_id` variable to our data which allows users to link our data to external political party data sources with this unique identifier.

Further, the `name.id` variable found in each file is another unique identifier for each MP. This variable was parsed directly from the Hansard XML files, and can be found in the Australian Parliamentary Handbook. As such, our data records can be integrated with those from the `ausPH` package which provides datasets for contents of the Australian Parliamentary Handbook. This will allow for convenient extraction of further details on each MP in a tidy, ready to analyze format.

@@

The code written to build this database is available on the GitHub repository associated with this paper (https://github.com/lindsaykatz/hansard-proj). All scripts were created using R software [@r_software]. The core packages used to develop these scripts are: the `XML` package @XML_pkg, the `xml2` package @xml2_pkg, the `tidyverse` R packages @tidyverse, the `AustralianPoliticians` package @auspol, and the `ausPH` package. `XML` and `xml2` were used for parsing the XML documents, `AustralianPoliticians` and `ausPH` were used for cleaning up and filling in MP details in the datasets, and `tidyverse` packages were used in all steps, for tidy wrangling of data.
